ckanr
=====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE,
  message = FALSE
)
```

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R-check](https://github.com/ropensci/ckanr/actions/workflows/R-check.yaml/badge.svg)](https://github.com/ropensci/ckanr/actions/workflows/R-check.yaml)
[![rstudio mirror downloads](https://cranlogs.r-pkg.org/badges/ckanr?color=FAB657)](https://github.com/r-hub/cranlogs.app)
[![cran version](https://www.r-pkg.org/badges/version/ckanr)](https://cran.r-project.org/package=ckanr)
[![codecov](https://codecov.io/gh/ropensci/ckanr/branch/main/graph/badge.svg?token=96K7ZIOmCB)](https://codecov.io/gh/ropensci/ckanr)

`ckanr` is an R client package for the [CKAN API](https://ckan.org/).
R users use it with CKAN data portals to read, write, and manage datasets.
The package wraps the entire CKAN REST API in R functions by resource type
(packages, resources, organizations, groups, users, tags).

## Description

CKAN is an open-source DMS (data management system) for data hubs and data portals.
Users publish, share and use data with CKAN. It powers hundreds of data portals worldwide.

`ckanr` works with those CKAN websites. Users create, modify, and manage
datasets. Users search and download existing data. Users then analyze the data in
R (stats/plotting/etc.). It works with any CKAN instance.

`ckanr` works for and is tested against
- the [CKAN v2.11 API](https://docs.ckan.org/en/2.11/api/),
- the [CKAN v2.10 API](https://docs.ckan.org/en/2.10/api/), and
- the [CKAN v2.9 API](https://docs.ckan.org/en/2.9/api/).

`ckanr` can work with older and newer CKAN versions.

Get started: <https://docs.ropensci.org/ckanr/>

## Installation

Stable CRAN version

```{r eval=FALSE}
install.packages("ckanr")
```

Development version

```{r eval=FALSE}
# From source
install.packages("remotes")
remotes::install_github("ropensci/ckanr")
# Binary via the rOpenSci universe
options(
  repos = c(
    ropensci = "https://ropensci.r-universe.dev",
    CRAN = "https://cloud.r-project.org"
  )
)
install.packages("ckanr")
```

```{r}
library("ckanr")
```

The default base CKAN URL is <https://demo.ckan.org/>
Functions that write to CKAN also require a privileged
CKAN API key.
To change the URL or key, use `ckanr_setup()`, or change the URL with the `url`
parameter in each function call.
To set one or both, run:

```{r}
ckanr_setup() # restores default CKAN url to https://demo.ckan.org/
ckanr_setup(url = "https://demo.ckan.org/")
ckanr_setup(url = "https://demo.ckan.org/", key = "my-ckan-api-key")
```

## ckanr package API

Each CKAN thing (package, resource, etc.) has a set of
functions in this package. For each CKAN thing, most functions return an S3 class,
and most other functions accept it. This helps piping. The following list shows the function groups for certain CKAN
things, with the prefix for the functions for that thing, and the name of the S3 class:

+ Packages (aka packages) - `package_*()` - `ckan_package`
+ Resources - `resource_*()` - `ckan_resource`
+ Related - `related_*()` - `ckan_related`
+ Users - `user_*()` - `ckan_user`
+ Groups - `group_*()` - `ckan_group`
+ Tags - `tag_*()` - `ckan_tag`
+ Organizations - `organization_*()` - `ckan_organization`

The S3 class objects all look very similar. For example:

```r
<CKAN Resource> 8abc92ad-7379-4fb8-bba0-549f38a26ddb
  Name: Data From Digital Portal
  Description:
  Creator/Modified: 2015-08-18T19:20:59.732601 / 2015-08-18T19:20:59.657943
  Size:
  Format: CSV
```

All classes state the type of object. They show the ID to the right of the type. They then show
a set of key-value fields. This printed object is a summary
of an R list, so you can index to specific values (for example, `result$description`).
If printed summaries miss important fields, let us know.

> note: This file keeps examples brief

## Contributors

(alphabetical)

* Florian Mayer
* Francisco Alves
* Hanna Böhner
* Imanuel Costigan
* Scott Chamberlain (original creator)
* Sharla Gelfand
* Wush Wu

## Meta

* [Report any issues or bugs](https://github.com/ropensci/ckanr/issues).
* License: MIT
* Get citation information for `ckanr` in R with `citation(package = 'ckanr')`
* This package follows a
  [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/).
  By contributing to this project, you agree to abide by its terms.
* If you want to contribute to package development, see the
  [contributing guide](https://docs.ropensci.org/ckanr/CONTRIBUTING.html).
