ckanr
=====

```{r echo=FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE
)
```

`ckanr` is an R client for the generic CKAN API - that is, plug in a base url for the CKAN instance of interest. 

## Installation

```{r eval=FALSE}
install.packages("devtools")
devtools::install_github("sckott/ckanr")
```

```{r}
library('ckanr')
```

> Note: the default URL is for http://data.techno-science.ca/. You can change that in the `url` parameter

## Changes

```{r}
changes(limit = 2, as = "table")
```

## List datasets

```{r}
datasets(as = "table")
```

## List tags

```{r}
tag_list('aviation', as='table')
```

## Show tags

Subset for readme brevity

```{r}
tag_show('Aviation')$packages[[1]][1:3]	
```

## List groups

```{r}
group_list(as='table')
```

## Show groups

Subset for readme brevity

```{r}
group_show('communications', as='table')$users
```

## Show a package

```{r}
package_show('34d60b13-1fd5-430e-b0ec-c8bc7f4841cf', as='table')$resources
```

## Search for packages

```{r}
out <- package_search(q = '*:*', rows = 2, as="table")$results
out[, !names(out) %in% 'resources']
```

## Search for resources

```{r}
resource_search(q = 'name:data', limit = 2, as='table')
```
