<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{ckanr vignette}
%\VignetteEncoding{UTF-8}
-->

```{r echo=FALSE}
library("knitr")
hook_output <- knitr::knit_hooks$get("output")
knitr::knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL, 
            x[lines], 
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
 })

knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  warning = FALSE, 
  message = FALSE
)
```

ckanr vignette
==============

## Install

Stable version from CRAN

```{r eval=FALSE}
install.packages("ckanr")
```

Development version from GitHub

```{r eval=FALSE}
devtools::install_github("ropensci/ckanr")
```

```{r}
library("ckanr")
```

Note: the default base CKAN URL is set to [http://data.techno-science.ca/](http://data.techno-science.ca/). You can change this using `ckanr_setup()`, or change the URL using the `url` 
parameter in each function call.

To set one or both, run:

```{r eval=FALSE}
# restores default CKAN url to http://data.techno-science.ca/
ckanr_setup() 
# Just set url
ckanr_setup(url = "http://data.techno-science.ca/")
# set url and key
ckanr_setup(url = "http://data.techno-science.ca/", key = "my-ckan-api-key")
```

## Changes

```{r}
changes(limit = 2, as = "table")[, 1:4]
```

## List datasets

```{r output.lines=1:10}
package_list(as = "table")
```

## List tags

```{r}
tag_list('aviation', as = 'table')
```

## Show tags

Subset for readme brevity

```{r}
tag_show('Aviation')
```

## List groups

```{r}
group_list(as = 'table')[, 1:3]
```

## Show groups

Subset for readme brevity

```{r}
group_show('communications', as = 'table')$users
```

## Show a package

```{r}
package_show('34d60b13-1fd5-430e-b0ec-c8bc7f4841cf', as = 'table')$resources[, 1:10]
```

## Search for packages

```{r}
out <- package_search(q = '*:*', rows = 2, as = "table")$results
out[, !names(out) %in% 'resources'][, 1:10]
```

## Search for resources

```{r}
resource_search(q = 'name:data', limit = 2, as = 'table')
```

## Example of using a different CKAN API

### The UK Natural History Museum

Website: [http://data.nhm.ac.uk/](http://data.nhm.ac.uk/)

List datasets

```{r output.lines=1:10}
ckanr_setup(url = "http://data.nhm.ac.uk")
package_list(as = "table")
```

Tags

_list_

```{r}
head(tag_list(as = "table"))
```

_show_

```{r}
tag_show('arthropods', as = 'table')
```

Packages

_search_

```{r}
out <- package_search(q = '*:*', rows = 2, as = 'table')
out$results[, 1:10]
```

_show_

```{r output.lines=1:10}
package_show(id = "56e711e6-c847-4f99-915a-6894bb5c5dea", as = "table")
```
